% Autogenerated translation of _index.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\renewcommand*\familydefault{\sfdefault}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}
\Large

\hrule
\chapter*{Display name}

name: Jian Zhang

\chapter*{Username (this should match the folder name)}

authors:
- admin

\chapter*{Is this the primary user of the site?}

superuser: true

\chapter*{Role/position}

role: Ph.D. Candidate \texttt{$<$br/$>$} School of Electrical Engineering and Telecommunications 

\chapter*{Organizations/Affiliations}

organizations:
- name: The University of New South Wales
  url: ""

\chapter*{Short bio (displayed in user profile at end of posts)}

bio: My research interests include autonomous robots, hybrid dynamical systems, machine learning and intelligent systems.

interests:
- Robotics
- Machine Learning
- Control Theories

education:
  courses:
  - course: PhD Candidate in Electrical Engineering
    institution: University of New South Wales
    year: 2017 to present
  - course: BSc in Electrical Engineering
    institution: Kennesaw State University
    year: 2016
  - course: BEng in Material Formation and Control Engineering
    institution: North China University of Technology
    year: 2016

\chapter*{Social/Academic Networking}

\chapter*{For available icons, see: https://sourcethemes.com/academic/docs/page-builder/\#icons}

\chapter*{For an email link, use "fas" icon pack, "envelope" icon, and a link in the}

\chapter*{form "mailto:your-email@example.com" or "\#contact" for contact widget.}

social:
- icon: envelope
  icon\emph{pack: fas
  link: 'mailto:jian.zhang4@unsw.edu.au'  \# For a direct email link, use "mailto:test@example.org".
- icon: google-scholar
  icon}pack: ai
  link: https://scholar.google.co.kr/citations?hl=en\&user=7xLCPN0AAAAJ
- icon: github
  icon\_pack: fab
  link: https://github.com/jianzhang6

\chapter*{Link to a PDF of your resume/CV from the About widget.}

\chapter*{To enable, copy your resume/CV to \texttt{static/files/cv.pdf} and uncomment the lines below.}

\chapter*{- icon: cv}

\chapter*{icon\_pack: ai}

\chapter*{link: files/cv.pdf}

\chapter*{Enter email to display Gravatar (if Gravatar enabled in Config)}

email: ""

\chapter*{Organizational groups that you belong to (for People widget)}

\chapter*{Set this to \texttt{[]} or comment out if you are not using People widget.}

user\_groups:
- Researchers

\section*{- Visitors}

\textbf{Jian Zhang} is currently a Ph.D. Candidate with the School of Electrical Engineering and Telecommunications, University of New South Wales (UNSW), Australia. She received her B.Sc. (Magna Cum Laude) degree in Electrical Engineering in 2016 from Kennesaw State University, Georgia, USA. Her current research interests include machine learning and intelligent control, hybrid systems, navigation, and control of mobile robots.

\end{document}
